---
title: "Personal Report Workflow"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Personal Report Workflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

This vignette focuses on the report-first personal workflow: start from a
single report, identify your character inside that report, and then pull the
events you care about.

```{r setup, eval = FALSE}
library(wclR)

client <- wcl_client()
report_code <- wcl_report_code("ZXaDV9FcAtyWnJPg")
fights <- wcl_fights(report_code, client = client)
actors <- wcl_actors(report_code, type = "player", client = client)
```

## Find a character inside the report

```{r actor-filter, eval = FALSE}
my_actor <- dplyr::filter(actors, name == "Vivax")
fight_id <- fights$fightID[[1]]
```

## Pull personal events

```{r personal-events, eval = FALSE}
casts <- wcl_events(
  report_code,
  fight_id = fight_id,
  data_type = "Casts",
  source_id = my_actor$actorID[[1]],
  include_resources = FALSE,
  client = client
)

buffs <- wcl_events(
  report_code,
  fight_id = fight_id,
  data_type = "Buffs",
  target_id = my_actor$actorID[[1]],
  include_resources = FALSE,
  client = client
)

pull_auras <- wcl_events(
  report_code,
  fight_id = fight_id,
  data_type = "CombatantInfo",
  hostility_type = "Friendlies",
  include_resources = FALSE,
  client = client
)

my_buff_uptime <- wcl_aura_uptime(
  buffs,
  combatant_info = pull_auras,
  target_ids = my_actor$actorID[[1]]
)

my_buff_intervals <- wcl_aura_uptime(
  buffs,
  combatant_info = pull_auras,
  target_ids = my_actor$actorID[[1]],
  output = "intervals"
)

casts <- wcl_join_actors(casts, actors)
casts <- wcl_add_relative_time(casts)
```

`wcl_aura_uptime()` uses the full fight as its denominator. Pull-time
CombatantInfo establishes buffs that were already present when combat began;
a snapshot with no later removal counts as 100% uptime. Fetch CombatantInfo
without an ability filter because its aura abilities are nested inside the
snapshot payload. Keep pagination enabled and avoid narrowing the event time
range: uptime needs every apply, refresh, stack, and remove event in the fight.
The Buffs request uses `target_id`, so it includes auras from every caster that
affected the selected player.

## Analyze movement and interrupted casts

Fetch positional casts with resources enabled, and fetch interrupts separately
so interruptions received by the actor are not lost to a source-only filter:

```{r movement-casts, eval = FALSE}
position_casts <- wcl_events(
  report_code,
  fight_id = fight_id,
  data_type = "Casts",
  source_id = my_actor$actorID[[1]],
  include_resources = TRUE,
  client = client
)

interrupt_events <- wcl_events(
  report_code,
  fight_id = fight_id,
  data_type = "Interrupts",
  client = client
)

movement <- wcl_actor_movement(
  position_casts,
  actor_ids = my_actor$actorID[[1]]
)

movement_track <- wcl_actor_movement(
  position_casts,
  actor_ids = my_actor$actorID[[1]],
  output = "track"
)

target_actor_id <- 44L
impact_events <- wcl_events(
  report_code,
  fight_id = fight_id,
  data_type = "DamageDone",
  hostility_type = "Enemies",
  source_id = my_actor$actorID[[1]],
  target_id = target_actor_id,
  include_resources = TRUE,
  client = client
)

target_track <- wcl_actor_movement(
  impact_events,
  actor_ids = target_actor_id,
  output = "track"
)

separation <- wcl_actor_distance(movement_track, target_track)

interruptions <- wcl_cast_interruptions(
  position_casts,
  interrupt_events = interrupt_events,
  source_ids = my_actor$actorID[[1]]
)

travel_time <- wcl_spell_travel_time(
  position_casts,
  impact_events,
  max_travel_ms = 5000,
  source_ids = my_actor$actorID[[1]],
  target_ids = target_actor_id
)
```

Movement uses sampled 2-D positions and is therefore a lower bound on the
actual path. Actor distance reports observed-overlap and full-fight coverage.
`wcl_cast_interruptions()` keeps explicit interrupt events and unfinished
`begincast` inferences in separate result columns. Travel time uses direct,
non-periodic landings inside the required maximum window.

## Notes

- v1 keeps personal workflows report-first on purpose.
- `wcl_filter_abilities()`, `wcl_filter_types()`, and `wcl_filter_and()` are
  narrow builders for common filter-expression fragments. The full syntax is
  documented in the [WCL expression guide](https://www.warcraftlogs.com/help/pins).
- `filter_expression` is WCL's SQL-like site language, not GraphQL, and filters
  event rows rather than response columns. Parenthesize multi-type `or`
  fragments before combining them with `wcl_filter_and()`.
- `include_resources`, `use_ability_ids`, and `use_actor_ids` control coarse
  event payload details. Arbitrary nested event JSON columns cannot be excluded
  server-side by column name.
- Character and guild discovery across reports can still be reached through
  `wcl_query_custom()` plus `wcl_request()` when needed.
- Use the [official Warcraft Logs v2 Warcraft schema](https://www.warcraftlogs.com/v2-api-docs/warcraft/)
  when building those custom queries.
