---
title: "Personal Report Workflow"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Personal Report Workflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

This vignette focuses on the report-first personal workflow: start from a
single report, identify your character inside that report, and then pull the
events you care about.

```{r setup, eval = FALSE}
library(wclR)

client <- wcl_client()
report_code <- wcl_report_code("ZXaDV9FcAtyWnJPg")
fights <- wcl_fights(report_code, client = client)
actors <- wcl_actors(report_code, type = "player", client = client)
```

## Find a character inside the report

```{r actor-filter, eval = FALSE}
my_actor <- dplyr::filter(actors, name == "Vivax")
fight_id <- fights$fightID[[1]]
```

## Pull personal events

```{r personal-events, eval = FALSE}
casts <- wcl_events(
  report_code,
  fight_id = fight_id,
  data_type = "Casts",
  source_id = my_actor$actorID[[1]],
  client = client
)

buffs <- wcl_events(
  report_code,
  fight_id = fight_id,
  data_type = "Buffs",
  source_id = my_actor$actorID[[1]],
  client = client
)

casts <- wcl_join_actors(casts, actors)
casts <- wcl_add_relative_time(casts)
```

## Notes

- v1 keeps personal workflows report-first on purpose.
- `wcl_filter_abilities()`, `wcl_filter_types()`, and `wcl_filter_and()` are
  the package-native way to build common filter expressions.
- Character and guild discovery across reports can still be reached through
  `wcl_query_custom()` plus `wcl_request()` when needed.
