---
title: "Population Workflow"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Population Workflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

This vignette shows a public-log crawl workflow for users looking at encounter
populations, rankings, and broad fight samples across many reports.

```{r setup, eval = FALSE}
library(wclR)

client <- wcl_client()
```

## Crawl public reports for a zone

```{r reports, eval = FALSE}
first_three_pages <- wcl_reports(
  zone_id = 1020,
  client = client
)

first_page <- wcl_reports(
  zone_id = 1020,
  pages = 1,
  client = client
)

all_requested_pages <- wcl_reports(
  zone_id = 1020,
  pages = 1:8,
  on_empty_page = "continue",
  client = client
)

zone_fights <- wcl_zone_fights(
  zone_id = 1020,
  pages = 1:3,
  client = client
)
```

`wcl_reports()` retrieves pages `1:3` by default; pass `pages = 1` to request
only the first page. Each completed page reports its page count and running
total in the form `Report page <page>: <page count> reports (<running total>
total).` Requested page numbers above 25 warn before retrieval and are capped
to page 25. By default, an empty page or reliable terminal metadata stops the
crawl and returns all reports collected so far. Use `on_empty_page = "ask"`
for an interactive decision or `"continue"` to traverse every explicit page.
`wcl_zone_fights()` accepts and forwards the same policy.

## Pull zone rankings

```{r rankings, eval = FALSE}
zone_rankings <- wcl_rankings_set(
  zone_id = 1018,
  metrics = c("speed", "progress", "execution"),
  pages = 1:3,
  client = client
)
```

## Notes

- `wcl_zone_fights()` wraps `wcl_reports()`, `wcl_fights()`, and optional
  `wcl_distinct_fights()` for population crawls.
- `wcl_rankings_set()` returns one row per ranking entry across multiple
  metrics and pages.
- `wcl_rankings()` remains available when you only need one zone leaderboard
  metric. These functions query zone encounter leaderboards;
  `wcl_report_rankings()` is the separate helper for rankings inside a specific
  uploaded report.
