---
title: "Population Workflow"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Population Workflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

This vignette shows a public-log crawl workflow for users looking at encounter
populations, rankings, and broad fight samples across many reports.

```{r setup, eval = FALSE}
library(wclR)

client <- wcl_client()
```

## Crawl public reports for a zone

```{r reports, eval = FALSE}
zone_fights <- wcl_zone_fights(
  zone_id = 1020,
  pages = 1:5,
  client = client
)
```

## Pull rankings

```{r rankings, eval = FALSE}
rankings <- wcl_rankings_set(
  zone_id = 1018,
  metrics = c("speed", "progress", "execution"),
  page = 1:3,
  client = client
)
```

## Notes

- `wcl_zone_fights()` wraps `wcl_reports()`, `wcl_fights()`, and optional
  `wcl_distinct_fights()` for population crawls.
- `wcl_rankings_set()` returns one row per ranking entry across multiple
  metrics and pages.
- `wcl_rankings()` remains available when you only need one metric.
