---
title: "Raid Report Workflow"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Raid Report Workflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

This vignette shows the main report-first workflow for raid teams that want to
inspect a specific log, drill into its fights, and then fetch the events and
player context needed for mechanics analysis.

```{r setup, eval = FALSE}
library(wclR)

client <- wcl_client()
report_code <- wcl_report_code("https://classic.warcraftlogs.com/reports/ZXaDV9FcAtyWnJPg")
```

## Discover the report structure

```{r fights, eval = FALSE}
fights <- wcl_fights(report_code, client = client)
actors <- wcl_actors(report_code, client = client)
```

## Pull role and roster information for one fight

```{r players, eval = FALSE}
fight_id <- fights$fightID[[1]]

players <- wcl_player_details(
  report_code,
  fight_id = fight_id,
  client = client
)
```

## Pull filtered events for mechanics analysis

```{r events, eval = FALSE}
damage_taken <- wcl_events(
  report_code,
  fight_id = fight_id,
  data_type = "DamageTaken",
  hostility_type = "Friendlies",
  include_resources = FALSE,
  use_ability_ids = TRUE,
  use_actor_ids = TRUE,
  filter_expression = wcl_filter_and(
    wcl_filter_abilities(70911),
    wcl_filter_types("damage")
  ),
  client = client
)
```

The three bandwidth controls default to `TRUE`. Set `include_resources`,
`use_ability_ids`, or `use_actor_ids` to `FALSE` when that detailed payload is
not needed. Event `data` is a JSON scalar in the API, so arbitrary nested
columns such as `classResources` cannot be excluded from the server response by
column name; they can only be dropped from the tibble after download. Disabling
an ID flag can also change which corresponding detail or ID columns are present.

## Pull rankings for the report or selected fights

```{r report-rankings, eval = FALSE}
all_rankings <- wcl_report_rankings(
  report_code,
  player_metric = "dps",
  client = client
)

fight_rankings <- wcl_report_rankings(
  report_code,
  fight_ids = fight_id,
  player_metric = "dps",
  client = client
)

raw_fight_rankings <- wcl_report_rankings(
  report_code,
  fight_ids = fight_id,
  output = "raw",
  client = client
)
```

With `fight_ids = NULL`, the default, Warcraft Logs returns rankings for the
whole report as individual fight rankings, not as one aggregate report rank.
The default `output = "tidy"` produces one row per ranked character and fight;
`output = "raw"` preserves the exact parsed rankings JSON. This report-level
helper is distinct from `wcl_rankings()`, which retrieves zone encounter
leaderboards.

Tidy output includes `segments`, `exportedSegments`, and `rankings_complete`.
The helper warns if Warcraft Logs has not yet processed every uploaded segment
for rankings. See the [rankings and parses guide](https://www.warcraftlogs.com/help/ranks/)
for the comparison and timeframe terminology.

## Enrich events with roster and actor context

```{r joins, eval = FALSE}
damage_taken <- wcl_join_actors(damage_taken, actors)
damage_taken <- wcl_join_players(damage_taken, players)
damage_taken <- wcl_add_relative_time(damage_taken)
```

## Notes

- `wcl_events()` paginates automatically with `nextPageTimestamp`.
- `wcl_player_details()` returns a single tidy table with a `role` column.
- `wcl_join_actors()` and `wcl_join_players()` let raid-review workflows stay
  retrieval-first without reimplementing joins in each notebook.
- `wcl_report_code()` accepts either a bare code or a full report URL.
- The [official Warcraft Logs v2 Warcraft schema](https://www.warcraftlogs.com/v2-api-docs/warcraft/)
  documents the fields, arguments, and enums available for custom queries.
