---
title: "Raid Report Workflow"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Raid Report Workflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

This vignette shows the main report-first workflow for raid teams that want to
inspect a specific log, drill into its fights, and then fetch the events and
player context needed for mechanics analysis.

```{r setup, eval = FALSE}
library(wclR)

client <- wcl_client()
report_code <- wcl_report_code("https://classic.warcraftlogs.com/reports/ZXaDV9FcAtyWnJPg")
```

## Discover the report structure

```{r fights, eval = FALSE}
fights <- wcl_fights(report_code, client = client)
actors <- wcl_actors(report_code, client = client)
```

## Pull role and roster information for one fight

```{r players, eval = FALSE}
fight_id <- fights$fightID[[1]]

players <- wcl_player_details(
  report_code,
  fight_id = fight_id,
  client = client
)
```

## Pull filtered events for mechanics analysis

```{r events, eval = FALSE}
damage_taken <- wcl_events(
  report_code,
  fight_id = fight_id,
  data_type = "DamageTaken",
  hostility_type = "Friendlies",
  filter_expression = wcl_filter_and(
    wcl_filter_abilities(70911),
    wcl_filter_types("damage")
  ),
  client = client
)
```

## Enrich events with roster and actor context

```{r joins, eval = FALSE}
damage_taken <- wcl_join_actors(damage_taken, actors)
damage_taken <- wcl_join_players(damage_taken, players)
damage_taken <- wcl_add_relative_time(damage_taken)
```

## Notes

- `wcl_events()` paginates automatically with `nextPageTimestamp`.
- `wcl_player_details()` returns a single tidy table with a `role` column.
- `wcl_join_actors()` and `wcl_join_players()` let raid-review workflows stay
  retrieval-first without reimplementing joins in each notebook.
- `wcl_report_code()` accepts either a bare code or a full report URL.
